Home

### 2021-08-02 analysis/index.Rmd
refactor: move common yaml headers into _site.yml

---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'home.bib')`"
---

>>>>

---
title: "Home"
site: workflowr::wflow_site
output:
  bookdown::html_document2:
    toc: false
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'rpackages', 'home.bib')`"
---
